### 2019-02-18 sections/intuition.tex
remove dead code
vending machine

\begin{example}[Vending machine]
\label{Vending machine}
% The following \CSP program models a vending machine that dispenses a small biscuit for one coin and a large biscuit for two coins. \todo{remove CSP?}
% \begin{equation*}
%   \textit{coin} \to (\textit{small} \to \text{STOP} \mid \textit{coin} \to \textit{large} \to \text{STOP})
% \end{equation*}
% % An equivalent reactive system in \ESTEREL could be defined as\fixme{validate}
% % \begin{equation*}
%   % V_\text{\ESTEREL} = \text{await } \textit{coin}; ( \text{await } \textit{button}; \text{emit } \textit{small} \parallel \text{await } \textit{coin}; \text{await } \textit{button}; \text{emit } \textit{large})
% % \end{equation*}
% A vending machine in \TOPHAT that is close in spirit to the one above looks as follows.

This example demonstrates external communication and choice.
A vending machine in \TOPHAT that dispenses a small biscuit for one coin and a large biscuit for two coins can be specified as follows
\begin{TASK}
  let vend : Task String = enter Int >>? \n. if n == 1 then edit "small"
    else if n == 2 then edit "large"
    else fail
\end{TASK}
The task asks the user to enter an amount of money.
This editor stands for a coin slot in a real machine that freely accepts and returns coins.
There is a continue button that is initially disabled, due to the fact that the right hand side of the step combinator results in $\Fail$.
When the user has inserted exactly 1 or 2 coins, the continue button becomes enabled.
When the user presses the continue button, the machine dispenses either a large or a small biscuit, depending on the amount of money.

% This machine does not exhibit exactly the same behaviour as the ones in \CSP, nor is it intended to.
% Instead, it just demonstrates how the same choice
%%NOTE: Problem is already stated --TS
% of buying a small biscuit for one coin or a large biscuit for two coins
% can be expressed in \TOPHAT.
\end{example}

>>>>

\begin{example}[Vending machine]
\label{Vending machine}

This example demonstrates external communication and choice.
It is a vending machine that dispenses a small biscuit for one coin and a large biscuit for two coins.
\begin{TASK}
  let vend : Task String = enter Int >>? \n. if n == 1 then edit "small"
    else if n == 2 then edit "large"
    else fail
\end{TASK}
The editor $\Enter \Int$ asks the user to enter an amount of money.
This editor stands for a coin slot in a real machine that freely accepts and returns coins.
There is a continue button that is initially disabled, due to the fact that the right hand side of the step combinator results in $\Fail$.
When the user has inserted exactly 1 or 2 coins, the continue button becomes enabled.
When the user presses the continue button, the machine dispenses either a large or a small biscuit, depending on the amount of money. \qed
